\newpage
 
\addcontentsline{toc}{section}{Bibliografia}
\begin{thebibliography}{}
	\bibitem{litlink1} Cezariusz Jastrzębski, Daniel J. Jastrzebski, Vitali Kozak, Karolina Pietak, Wojciech Gebicki $"$Synthesis and structural characterization of thin $\mathbf{Ga_{2}S_{3}}$ layers on semiconducting $\mathbf{GaP}$ substrate$"$, złożone do Journal: Materials Science in Semiconductor Processing, 2018.
	
	\bibitem{litlink2} $\mathbf{Ga_{2}S_{3}}$ Zeitschrift für Kristallographie - New Crystal Structures, 216, 327-328 (2001)
	
	\bibitem{litlink3} Adrian Kamiński, Instytut Fizyki UAM $"$Spektroskopia Ramana – drgania i widmo rozpraszania$"$
	
	\bibitem{litlink4} Kacper Grodecki1 $"$Spektroskopia ramanowska grafenu$"$
	
	\bibitem{litlink5} Momma K and Izumi F 2011 J. Appl. Crystallogr. 44 1272-1276
	
	\bibitem{litlink6} Ching-Hwa Ho1, Hsin-Hung Chen $"$Optically decomposed near-band-edge structure and excitonic transitions in
	$\mathbf{Ga_{2}S_{3}}$$"$ Sci. Rep. 4, 6143; DOI:10.1038/srep06143
	(2014).
	
	\bibitem{litlink7} H. F. Liu, K. K. Ansah Antwi, N. L. Yakovlev, H. R. Tan, L. T. Ong, S. J. Chua, D. Z. Chi $"$Synthesis and Phase Evolutions in Layered Structure of $\mathbf{Ga_{2}S_{3}}$ Semiconductor Thin Films on Epiready $\mathbf{GaAs}$ (111) Substrates$"$ ACS Appl. Mater. Interfaces 2014, 6, 3501-3507
	
	\bibitem{litlink8} Chang-Sun Yoon, F. D. Medina, L. Martinez, Tae-Young Park, Moon-Seog Jin, and Wha-Tek Kim $"$Blue photoluminescence of $\mathbf{\alpha-Ga_{2}S_{3}}$ and $\mathbf{\alpha-Ga_{2}S_{3}}:Fe^{2+} $sinle crystals$"$ Appl. Phys. Lett. 83, 1947 (2003)
	
	\bibitem{litlink9} I. Gulera,, M. Isik b, L. Gasanovac, A. Mahammadovc, N. Gasanly $"$Thermoluminescence in gallium sesquisulfide single crystals:
	usual and unusual heating rate dependencies$"$ Optik 165 (2018) 132–136
	
	\bibitem{litlink10} K.A. Kokh, Z.M. Huang, J.G. Huang, Y.Q. Gao, B. Uralbekov, J. Panomarev, I.N. Lapin, V.A. Svetlichnyi, G.V. Lanskii, Yu. M. Andreev $"$Study of $\mathbf{Ga_{2}S_{3}}$ crystals grown from melt and $\mathbf{PbCl_{2}}$ flux$"$ Materials Research Bulletin 84 (2016) 462–467
	
	\bibitem{litlink11} Tansir Ahamad and Saad M Alshehri $"$Green Synthesis and Characterization of Gallium(III) Sulphide $\mathbf{Ga_{2}S_{3}}$
	Nanoparicles at Room Temperature$"$ Nano Hybrids Vol. 6 (2014) 37-46
	
	\bibitem{litlink12} I. Carman, D. Rusu, E.R. Ardeleanu, I.Evtodiev $"$THE Detectors of UV and X radiation based on $\mathbf{Ga_{2}S_{3}}$ and $\mathbf{GaSe}$ semiconductors intercalated with $\mathbf{Cd}$$"$ Vol. 7, No. 1, January - March 2015, p. 27 - 32
	
	\bibitem{litlink13} H. F. Li K. K. Ansah Antw C. S. Chu J. Huang S. J. Chu and D. Z. Chia $"$Epitaxial Synthesis, Band Offset, and Photoelectrochemical
	Properties of Cubic $\mathbf{Ga_{2}S_{3}}$ Thin Films on $\mathbf{GaAs}$ (111) Substrates$"$ ECS Solid State Letters, 3 (11) P131-P135 (2014)
	 
	\bibitem{litlink14} Katerina M Othonos, Matthew Zervos, Constantinos Christofides and Andreas Othonos $"$Ultrafast Spectroscopy and Red Emission
	from $\beta-\mathbf{Ga_{2}O_{3}}/ \beta-\mathbf{Ga_{2}S_{3}}$ Nanowires$"$ Othonos et al. Nanoscale Research Letters (2015) 10:304
	
	\bibitem{litlink15} Ching-Hwa Ho, Min-Han Lin, Yi-Ping Wang, Ying-Sheng Huang $"$Synthesis of $\mathbf{In_{2}S_{3}}$ and $\mathbf{Ga_{2}S_{3}}$ crystals for oxygen sensing and UV photodetection$"$ Sensors and Actuators A 245 (2016) 119–126
	
	\bibitem{litlink16} S. R. Alharbi, A. F. Qasrawi $"$Dielectric Dispersion in $\mathbf{Ga_{2}S_{3}}$ Thin Films$"$ Plasmonics (2017) 12:1045–1049
	
	\bibitem{litlink17} A. N. Georgobiani, B. G. Tagiev, O. B. Tagiev, Kh. B. Ganbarova, and U. F. Kasumov $"$Photoluminescence and Raman Spectra of $\mathbf{(Ga_{2}S_{3})_{0.95}(Sm_{2}O_{3})_{0.05}} Crystals$$"$ Neorganicheskie Materialy, 2010, Vol. 46, No. 10, pp. 1172–1174.
	
	\bibitem{litlink18} I. Pethes, V. Nazabal, R. Chahal, B. Bureau, I, Kaban, S. Belin, P. Jówari $"$Local motifs in $\mathbf{GeS_{2}-Ga_{2}S_{3}}$ glasses$"$
	
	\bibitem{litlink19} S. Caramazza A. Collina, E. Stellino, P. Dore, and P. Postorino $"$Polarization analysis of first- and second-order Raman scattering from $\mathbf{MoTe_{2}}$ single crystal.$"$
	
	\bibitem{litlink20} Guihua Shang, Mark J. Hampden-Smith and Eileen N. Duesler $"$Synthesis and characterization of gallium thiocarboxylates as novel single-source precursors to gallium sulfide thin films by aerosol-assisted CVD$"$ Chem. Commun., 1996
	
	\bibitem{litlink21} Mike R. Lazel, Paul O’Brien, David J. Otway, and Jin-Ho Park $"$Deposition of Thin Films of Gallium Sulfide from a Novel Single-Source
	Precursor, $\mathbf{Ga(S_{2}CNMeHex)_{3}}$, by Low-Pressure Metal-Organic Chemical Vapor Deposition$"$ Chem. Mater. 1999, 11, 3430-3432
	
	\bibitem{litlink22} V.P. Mushjnskii, L.I. Palaki, and V.V. Chebotaru $"$Optical Absorption $\alpha-Ga_{2}S_{3}$ Single Crystals$"$ phys. stat. sol. (b) 83, K149 (1977)
	
	\bibitem{litlink23} A. Tomas, M. Guymon, M.P. Pardo, M. Guittard, and J. Flahau $"$X-Ray Diffraction and Electron Microscopy Studies of $\alpha-$ and $\beta$-$\mathbf{Ga_{2}S_{3}}$$"$ phys. stat. sol. (a) 107, 775 (1988)
	
	\bibitem{litlink24} Huseyin Ertap, Tarik Baydar, Mustafa Yuksek, Mevlut Karabulut $"$Structural and optical properties of gallium sulfide thin film$"$ Turk J Phys (2016) 40: 297-303
	
	\bibitem{litlink25} Zhiming Huang, J.-G. Huang, K.A. Kokh,c, V.A. Svetlichnyi, A.V. Shabalina, Yu.M. Andreev, and G.V. Lanskii. $"$$\mathbf{Ga_{2}S_{3}}$ - optical properties and perspectives for THz applications$"$
	 
	\bibitem{litlink26} Racoveţ O., Evtodiev I., Caraman Iu., Rotaru I, Lazăr G.
	$"$Optical Properties of Compounds with submicron points otained
	through $\mathbf{Ga_{2}S_{3}}$ intercalation with $\mathbf{Cd}$$"$  Procese, modele, experimente, nr. 2, 2012
	
	\bibitem{litlink27} Andrew R. Barron $"$Chalcogenides of Aluminum,
	Gallium, and Indium$"$ OpenStax-CNX module: m33044
	
	\bibitem{lilink28} J. Thorstensen, K. H. Haugholt, A. Ferber, K. A. H. Bakke, J. Tschudi $"$Low-cost resonant cavity Raman gas probe for multi-gas
	detection$"$ J. Europ. Opt. Soc. Rap. Public. 9, 14054 (2014)
	
	\bibitem{litlink29} C.Y. Jones J.C. Bryan, K. Kirschbaum and J. G. Edwards $"$Refinement of the crystal structure of digallium trisulfide, $\mathbf{Ga_{2}S_{3}}$$"$ Z. Kristallogr. NCS 216 (2001) 327-328
	
	\bibitem{litlink30} Christian Kranert, Chris Sturm, Rüdiger Schmidt-Grund and Marius Grundmann $"$Raman tensor elements of $\beta$-$\mathbf{Ga_{2}O_{3}}$$"$ Scientific Reports | 6:35964 | DOI: 10.1038/srep35964
	 
	\bibitem{litlink31} Tao Haizheng, Zhao Xiujian, Jing Chengbin, Yang Hui, Mao Shun $"$Raman scattering studies of the $\mathbf{GeS_{2}-Ga_{2}S_{3}-CsCl}$$"$ Solid State Communications 133 (2005) 327-332.
	
	\bibitem{litlink32} R. Rao, H. Chandrasekaran, S. Gubbala, M.K. Sunkara,
	C. Daraio, S. Jin, and A.M. Rao $"$Synthesis of Low-Melting Metal Oxide and
	Sulfide Nanowires and Nanobelts.$"$ Journal of ELECTRONIC MATERIALS, Vol. 35, No. 5, 2006
	
	\bibitem{litlink33} E.M. Marmolejo, E. Granado, O.L. Alves, C.L. Cesar, L.C. Barbosa $"$Spectroscopy and thermal properties of $\mathbf{Ga_{2}S_{3}}$ based glasses$"$ Journal of Non-Crystalline Solids 247 (1999) 189-195
	
	\bibitem{litlink34} Katerina M Othonos, Matthew Zervos, Constantinos Christofides and Andreas Othonos $"$Ultrafast Spectroscopy and Red Emission
	from $\beta-\mathbf{Ga_{2}O_{3}}/\beta-\mathbf{Ga_{2}S_{3}}$ Nanowires$"$ Othonos et al. Nanoscale Research Letters (2015) 10:304
	
	\bibitem{litlink35} Eman O. Nazzal, A. F. Qasrawi, S. R. Alharbi $"$Engineering the Optical and Dielectric Properties
	of the $\mathbf{Ga_{2}S_{3}/In/Ga_{2}S_{3}}$ Nanosandwiches via Indium Layer
	Thickness$"$
	
	\bibitem{litlink36} Jastrzębski Daniel, Praca inżynierska, Wydział Chemii Politechniki Warszawskiej, promotor prof. dr hab. inż. Sławomir Podsiadło
	
	\bibitem{litlink37} Daniel J. Jastrzebski, Karolina Pietak, Cezariusz Jastrzebski, Slawomir Podsiadlo, Syntesis of thin Ga2S3 layers on semiconducting substrates, EMRS, Fall Meeting 2018, Poster, Book of abstracts, \textbf{R.P2.13}
	
\end{thebibliography}














